---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MOMENT

<!-- badges: start -->
<!-- badges: end -->

MOMENT provides a set of ensemble machine learning algorithms that can successfully model multi-omics multi-class data. The algorithms are based on a technique known as late integration, training a machine learning model on each modality independently and aggregating the results in different ways to give a final prediction. 
In addition, MOMENT allows users to model individual modalities, a concatenation of all modalities or a selected subset of modalities, for comparison with the ensemble models, employing either classification or survival analysis. Furthermore, an incremental model can determine a minimal set of modalities for accurate modelling of the data and an exploration model allows the user to plot 2-dimensional representations of the data using principal component analysis (PCA), t-distributed stochastic neighbor embedding (t-SNE) or Uniform Manifold Approximation and Projection (UMAP).
MOMENT is fully customisable and highly flexible, using an object-oriented design. It allows the user to model multi-omics multi-class data, without the need for a detailed understanding of the specifics of machine learning, nor of the mlr (Machine Learning in R) package, on which MOMENT relies.

## Installation

Install `MOMENT` from CRAN, or you can install the development version of MOMENT from
[GitHub](https://github.com/) with:

``` r
devtools::install_github("annette987/MOMENT")
```

## Example

```{r example}
suppressMessages(library(MOMENT))
cc = make_config(system.file("extdata", "sample_config.xlsx", package = "MOMENT"))
vote_ens_h = MM_Voting$new(cc, decision = 'hard', subset = NULL, validate = FALSE)  
res_ens_h = vote_ens_h$learn()  
#
## basic example code
```

